---
title: "Activity: Nuclear Reactors"
author: "Sangeeta Iyer"
output: html_notebook
---

```{r}
library(tidyverse)

```

## Scrape the Data 

```{r}
#My code here.... 
library(rvest)

page <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

head(tableList[[21]])
Japan <- tableList[[21]]
Japan

Japan <-
  Japan %>%
  filter(row_number() > 1) %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         model = Model,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = Beginbuilding,
         operation = Commercialoperation, 
         closure = Closed)

str(Japan)
Japan

```
```{r}
Japan <- Japan %>%
  mutate(
    reactor = as.character(reactor),
    construction = lubridate::dmy(construction),
    operation = lubridate::dmy(operation),
    closure = lubridate::dmy(closure)
  )

Japan
```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

My answer here..... 
Each row seems to represent one case, a reactor, which is tidy. However, some of the variables names appear repetitive or are multiple words long, which is not tidy.   



## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
#my code here 
Japan


ggplot(Japan) +
  aes(x = construction, y = netMW, colour = Type) +
  geom_point() +
  scale_color_hue(direction = 1) +
  theme_minimal()

```

## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
#my code here... 

china <- tableList[[10]]

china

china <-
  china %>%
  filter(row_number() > 1) %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         model = Model,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = Beginbuilding,
         operation = Commercialoperation, 
         closure = Closed)


china <- china %>%
  mutate(
    construction = lubridate::dmy(construction),
    operation = lubridate::dmy(operation),
    country = 'China'
  )
china

Japan <- Japan %>%
  mutate(
    country = 'Japan'
  )

JapanChina <- rbind(Japan, china)
JapanChina

```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}
#My code here
Japan <- Japan %>%
  mutate(reactorid = paste(name, reactor))


ggplot(Japan) +
  geom_segment(data = Japan, mapping = aes(x = construction, y = reactorid, xend = operation, color = Type)) +
  scale_color_hue(direction = 1) +
  theme_minimal()
```
